---
title: "Mini-Project 2"
authors: "Margaret Perry, Kendra Swanson, Arielle Dror"
date: "March 24, 2017"
output: html_document
---


##Goal
The goal of this code is to tidy and graph the data to display the corrolations between the cortributions and the success of the candidate. We're focusing just on general House elections.

```{r, include=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r}
##Renaming columns for clarity and easier join
names(contributions)[names(contributions)=="name"] <- "cmte_name"

house_elections <- house_elections %>%
  mutate(candidate_name = toupper(candidate_name))
```

```{r}
## Function that produces candidate information by state and office in 2012 election cycle

office_state_cands <- function(office_arg, state_arg) {
  filter(candidates, cand_office == office_arg, cand_election_yr == "2012", cand_office_state == state_arg)
}

## Examples (delete/comment out in final submission)
CA_house <- office_state_cands(office_arg = "H", state_arg = "CA")
CA_house

pres_cands <- office_state_cands(office_arg = "P", state_arg = "US")
pres_cands

```

```{r}
## Functions that total COMMITTEE contributions for and contributions against each candidate
## in a given table of candidates. 

cand_for <- function(data_arg) {
  data_arg %>%
    left_join(contributions, by = "cand_id") %>%
    filter(transaction_amt > 0, transaction_type == "24K" | transaction_type == "24E" | transaction_type == "24F" | transaction_type == "24C" | transaction_type == "24Z") %>%
    group_by(cand_name) %>%
    summarize(total_for = sum(transaction_amt))
}

cand_against <- function(data_arg) {
  data_arg %>%
    left_join(contributions, by = "cand_id") %>%
    filter(transaction_amt > 0, transaction_type == "24A" | transaction_type == "24N") %>%
    group_by(cand_name) %>%
    summarize(total_against = sum(transaction_amt))
}


## Examples
CA_house_cand_for <- cand_for(data_arg = CA_house)
CA_house_cand_for

CA_house_cand_against <- cand_against(data_arg = CA_house)
CA_house_cand_against

```
Transaction codes: 24A, 24N = against; 24E, 24F, 24C, 24K, 24Z = for

```{r}
## Function that determines whether a candidate has won or lost given a table of candidates
## **Note: only works for house elections** 
cand_success <- function(data_arg) {
  data_arg %>%
    left_join(house_elections, by = c("cand_id" = "fec_id")) %>%
    select(cand_name, primary_votes, general_votes, ge_winner)
}
cand_success(data_arg = office_state_cands(office_arg = "H", state_arg = "CA"))

```


```{r}
## Function that joins for, against, success, and candidates table given a table of candidates
cand_info <- function(cand_table) {
  cand_table %>%
    left_join(cand_for(data_arg = cand_table), by = "cand_name") %>%
    full_join(cand_against(data_arg = cand_table), by = "cand_name") %>%
    left_join(cand_success(data_arg = cand_table), by = "cand_name") %>%
    mutate(total = ifelse(!is.na(total_against) & !is.na(total_for), total_for + total_against, 
                          ifelse(is.na(total_against), total_for, 
                                 ifelse(is.na(total_for), total_against, 0)))) %>%
    mutate(prop_against=(total_against/total)*100) %>%
    filter(total_for > 0 & total_against > 0 & general_votes > 0) %>%
    select(cand_id, cand_name, cand_party_affiliation, cand_state, cand_office, cand_office_district, total_for, total_against, total, general_votes, ge_winner, prop_against) %>%
  arrange((cand_office_district))
}


CA_house_cand_info <- cand_info(cand_table = office_state_cands(office_arg = "H", state_arg = "CA"))

CA_house_cand_info
```

```{r}
candidate_graphic_1 <- ggplot(CA_house_cand_info, aes(x=cand_name, y= total, fill=prop_against))+coord_flip()+geom_bar(stat="identity")+scale_fill_continuous(name= "Percentage of Donations\nAgainst Candidate", low="firebrick1", high = "firebrick4")+xlab("Candidate")+ylab("Total Donations")+scale_y_continuous(breaks = c(0, 2000000, 4000000, 6000000), labels = c("$0", "$2,000,000", "$4,000,000", "$6,000,000") ) + ggtitle("House Candidates in California with\nDonations For and Against")

candidate_graphic_1
```
```{r}
candidate_graphic_2 <- ggplot(CA_house_cand_info, aes(x=cand_name, y= total, fill=ge_winner))+coord_flip()+geom_bar(stat="identity")+xlab("Candidate")+ylab("Total Donations")+scale_y_continuous(breaks = c(0, 2000000, 4000000, 6000000), labels = c("$0", "$2,000,000", "$4,000,000", "$6,000,000") ) + scale_fill_discrete("Result", breaks=c("N", "W"), labels=c("Loss", "Win"))+ggtitle("Results of Elections of House Candidates")
candidate_graphic_2
```

Blog Post 

This graphic displays data for committees and individuals and their contributions to California candidates for House of Representatives in the year 2012. The final table presents a variety of variables that show the area of which the candidate represents, the total number of contributions, for and against, what the candidate was running for, the number of votes received, and whether or not the candidate won. The reasoning in combining the tables in this way was to create something in the way of a master table, and allowing us to store the majority of our relevant data into one concise location. From this table we were able to form two main data graphics. All the candidates displayed had a donation made against them. The first graph focuses on the percentage of contributions against the chosen candidates. This is shown through the graph's use of scaled color, the darker the red coloring the higher percentage of contributions against the candidate, while the bar shows the total contribution. The second graph shows whether or not a candidate won the election. 
The first graph shows an interesting observed correlation between the amount of total contributions and the percentage of the contributions that are against the candidate. The majority of the candidates with total contributions more than 2,000,000 have about 60% of their contributions were against them. An interesting observation is how in spite of this the majority of these candidates won. This can be because of the lack of people running against incumbents in the House, which would result in people winning regardless of contributions.  
In terms of future research and elaborations, I would like to view the situation by party, or a have graphs displaying the same data but separated by incumbents and non incumbents. 
